Weekday sleep, total cholestrol and the modifying effect of age on systolic blood pressure: An analysis of the 2015-2018 non-obese NHANES population

### 2023-12-11 manuscript/paper.Rmd
update

<!-- Beyond age, the basal metabolic rate (BMI) emerges as a recognized -->

<!-- contributor to systolic blood pressure (SBP), with individuals -->

<!-- exhibiting higher BMI values demonstrating a propensity for elevated -->

<!-- SBP. Gender also holds a discernible association with SBP dynamics. -->

<!-- Empirical evidence in CITE demonstrates that women typically manifest -->

<!-- lower SBP than men until the onset of menopause, after which women -->

<!-- exhibit higher SBP levels compared to men. Additionally, heightened -->

<!-- levels of cholesterol are closely linked to vascular damage. The -->

<!-- accumulation of cholesterol deposits and calcium within arteries -->

<!-- precipitates arterial stiffening, necessitating augmented cardiac -->

<!-- efforts to circulate blood, potentially culminating in elevated blood -->

<!-- pressure. This study endeavors to examine the interrelationships between -->

<!-- age and cholesterol levels, emphasizing consideration of potential -->

<!-- confounding variables. Table 1 comprehensively delineates the array of -->

<!-- variables under scrutiny, ensuring a comprehensive analysis of their -->

<!-- collective impact -->

# Methods

@@

### Exposures:

Sleep duration on workdays was evaluated by the questionnaire with the
following questions: "Number of hours usually sleep on weekdays or
workdays". We then categorized this variable into three groups, that is,
\< 6 h, 6--8 h, ≥ 8 h respectively, and used \< 6 h as the reference
group in our analysis. We also explored the association between total
cholestrol (in mmol/L) level on systolic blood pressure including
potential effect modification by other factors.

### Covariates:

In addition to the exposure and outcome variables, our analyses included
the following as covariates: Race divided into four groups as Mexican
American, white, black and other race. Alcohol consumption was grouped
into drinking, no drinking, not recorded. Smoking status as smoking, not
smoking, not recorded. Diabetes was defined as yes, no, borderline, or
not recorded. Hypertension was defined as yes, no, or not recorded.
Snorting was defined as yes, no, and not recorded. US citizenship status
was defined as citizen by birth or naturalization, don't know, not a
citizen, or refused to answer. Education level was grouped into four
categories including graduate studies, high school, less than grade 12
or some college. Additional covariates included marital status, gender,
age, albumin, creatinine,hemoglobin, total cholesterol (TC), aspertate
aminotransferase (AST), high-density lipoprotein (HDL), and body mass
index (BMI). Details about these variables can be found at
<https://wwwn.cdc.gov/nchs/nhanes/search/default.aspx>. Age, albumin,
creatinine, hemoglobin, TC, AST, HDL, and BMI were analyzed as
continuous variables whereas gender, alcohol consumption, diabetes,
smoking, race, hypertension, and snorting were analyzed as categorical
variables. Table \@ref{tab:tabone} highlights the variable names and
descriptions as utilized in this study.

@@

```{=tex}
\begin{table}

@@

# Discussion and conclusion

>>>>

```{=html}
<!-- Beyond age, the basal metabolic rate (BMI) emerges as a recognized
contributor to systolic blood pressure (SBP), with individuals
exhibiting higher BMI values demonstrating a propensity for elevated
SBP. Gender also holds a discernible association with SBP dynamics.
Empirical evidence in CITE demonstrates that women typically manifest
lower SBP than men until the onset of menopause, after which women
exhibit higher SBP levels compared to men. Additionally, heightened
levels of cholesterol are closely linked to vascular damage. The
accumulation of cholesterol deposits and calcium within arteries
precipitates arterial stiffening, necessitating augmented cardiac
efforts to circulate blood, potentially culminating in elevated blood
pressure. This study endeavors to examine the interrelationships between
age and cholesterol levels, emphasizing consideration of potential
confounding variables. Table 1 comprehensively delineates the array of
variables under scrutiny, ensuring a comprehensive analysis of their
collective impact. -->
```
# Methods

@@

```{=html}
<!-- 
### Exposures:

Sleep duration on workdays was evaluated by the questionnaire with the
following questions: "Number of hours usually sleep on weekdays or
workdays". We then categorized this variable into three groups, that is,
\< 6 h, 6--8 h, ≥ 8 h respectively, and used \< 6 h as the reference
group in our analysis. We also explored the association between total
cholestrol (in mmol/L) level on systolic blood pressure including
potential effect modification by other factors.
-->
```
### Covariates:

```{=html}
<!-- Sleep duration on workdays was evaluated by the questionnaire with the
following questions: "Number of hours usually sleep on weekdays or
workdays". We then categorized this variable into three groups, that is,
\< 6 h, 6--8 h, ≥ 8 h respectively, and used \< 6 h as the reference
group in our analysis. -->
```
Our analyses included the following as covariates: Race divided into
four groups as Mexican American, white, black and other race. Alcohol
consumption was grouped into drinking, no drinking, not recorded.
Smoking status as smoking, not smoking, not recorded. Diabetes was
defined as yes, no, borderline, or not recorded. Hypertension was
defined as yes, no, or not recorded. Snorting was defined as yes, no,
and not recorded. US citizenship status was defined as citizen by birth
or naturalization, don't know, not a citizen, or refused to answer.
Education level was grouped into four categories including graduate
studies, high school, less than grade 12 or some college. Additional
covariates included marital status, gender, age, albumin,
creatinine,hemoglobin, total cholesterol (TC), aspertate
aminotransferase (AST), high-density lipoprotein (HDL), and body mass
index (BMI). Details about these variables can be found at
<https://wwwn.cdc.gov/nchs/nhanes/search/default.aspx>. Age, albumin,
creatinine, hemoglobin, TC, AST, HDL, and BMI were analyzed as
continuous variables whereas gender, alcohol consumption, diabetes,
smoking, race, hypertension, and snorting were analyzed as categorical
variables. Sleep duration on workdays was also recorded and was
categorized into three groups, that is, \< 6 h, 6--8 h, ≥ 8 h
respectively, and used \< 6 h as the reference group in our analysis.
Table \@ref{tab:tabone} highlights the variable names and descriptions
as utilized in this study.

@@

@@

# Conclussion

## Discussion

## Limitations

Our study encountered a significant challenge with missing data,
resulting in a notable reduction in our sample size. Despite initially
having a sample of \$n=19,225\$, the final analysis was conducted on a
considerably smaller sample of \$n=1,977\$ observations. This
substantial reduction in the sample size raises concerns about the
robustness and reliability of our findings. Addressing this issue
becomes crucial to ensure the validity of our study outcomes.

In response to this challenge, we propose the implementation of multiple
imputation techniques. This approach involves generating multiple
plausible sets of missing values based on observed data patterns. By
imputing missing values using this method, we aim to enhance the
completeness of our dataset. This strategy is intended to mitigate
potential biases resulting from missing data and fortify the reliability
and accuracy of our analytical outcomes.
